A Connection Between Star Formation Rate and Dark Matter Halos at $Z\sim6$ In 2013 Planck Cosmology.

### 2015-03-11 paper/methodology.tex
Methodology Dust Attenuation

%Dust Extinction
\subsection{MCMC}
We used a Markov Chain Monte Carlo method to find the best parameters and its 
uncertainties over each one of the boxes and each observational dataset.

@@

An UV luminosity is given to each halo as function of his mass according to equation
 \ref{eqn:luminosity}.
Luminosity is converted to magnitude using:
  \[ M_{U} = 51.82 - 2.5 \log_{10}(L_{U}). \]

>>>>

\subsection{Dust Attenuation}

Dust in star forming galaxies absorbs part of the UV radiation and reemits on IR. The more 
massive is the galaxy then more dust contains and dust attenuation will be greater. The 
relation between dust attenuation and magnitude have been already studied, with this relation 
we can infer the dust-free UV luminosity of a galaxy from observations, resulting in  a more 
accurate inferred SFR.

The UV Spectral Slope $\beta$ was introduced by \citet{meurer99} as a UV color to 
study dust attenuation in local starburst galaxies and extrapolating to high redshift galaxies. 
This index appears when a power law fitting is performed over the spectral flux $f$ 
as function of the wavelength $\lambda$;
\[ f \propto \lambda^\beta.\]
The relation for ultra-violet attenuation at $1600 \textrm{\AA}$ they found is:
\begin{equation}
A_{1600} = 4.43 + 1.99 \beta,
\end{equation}
with $A_{1600}$ in magnitude units.

Due LBGs have more similar spectra properties to local starburst galaxies rather than AGNs 
for example, we can assume that local calibration of $\beta-A_{1600}$ can be applied also 
for LBGs,
%%% From Meurer99
``The main requirement is that the data include fluxes in two broad bands or coarse spectra 
covering the rest-frame UV.''

\citet{bouwens12b} uses the fluxes on different bands to estimate $\beta$ on each LBG 
candidate found with $z \sim 4-7$. After in redshift groups they found a linear relation 
between $\beta$ and the UV magnitude:
\begin{equation}
\langle \beta \rangle = \frac{d \beta}{d M_{UV}} \left( M_{UV,AB}+19.5 \right) 
                                   + \beta_{M_{UV}=-19.5}
\end{equation}
with $ \beta_{M_{UV}=-19.5} = -2.20$ and $d \beta/d M_{UV} = -0.21$ at $z=5.9$.

\citet{smit12} used the aforementioned relations to infer the corrected luminosity functions,
i.e. dust-free luminosity functions, and the corrected SFR at $z=4$.

Here we use the inverse relation, starting from the intrinsic or dust-free galaxy magnitude, 
obtaining the observed magnitude:
\begin{equation}\label{eqn. dust attenuation}
  M_{obs} = \begin{cases} 
                         \frac{M_{int}-4.616}{1.259}, &\mbox{if } A>0 \\
                         M_{int}, &\mbox{else}
                   \end{cases}.
\end{equation}

\subsection{MCMC}
We used a Markov Chain Monte Carlo method to find the best parameters and its 
uncertainties over each one of the boxes and each observational dataset.

@@

An UV luminosity is given to each halo as function of his mass according to equation
 \ref{eqn:luminosity}.
Luminosity is converted to magnitude using:
  \[ M_{UV} = 51.82 - 2.5 \log_{10}(L_{UV}). \]
If we consider the dust attenuation im the equation \ref{eqn. dust attenuation} we have
a dust-corrected UV Luminosity Function.
